\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-02 write_up/mixfishsim_ecolmod.tex
text updated

Our study evaluates the importance of data scaling and considers potential bias
introduced through data aggregation when using commercial fisheries data to
infer spatio-temporal dynamics in fisheries. Understanding how fishers exploit
multiple heterogeneously distributed fish populations with different catch
limits or conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to species targeting in fisheries resulting in preferential sampling
\citep{Martinez-Minaya2018}. Often data is aggregated or extrapolated which
requires assumptions about the spatial and temporal scale of processes. Our
study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatio-temporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
\citep{Dunn2016}, understanding assumptions behind the data used -
increasingly a combination of logbook and positional information from vessel
monitoring systems - is vital to ensure measures are effective. \\

@@

Our approach captures fine scale population and fishery dynamics not usually
considered (although see \cite{Bastardie2010, Bailey2018}) which offers the
advantage that larger scale fishery patterns are emergent properties of the
system rather than the result of a statistical modelling framework. \\

WHAT'S ALREADY AVAILABLE - COMPARE AND CONTRAST

Our results show commercial data can provide at right scale and resolution -
depends on scale of process: pop movement etc... Important to consider how
fishers interact / adapt to changes with the resource and mgmt. \\

>>>>

Our study evaluates the importance of data scaling and considers potential bias
introduced through data aggregation when using fisheries data to infer
spatio-temporal dynamics of fish populations. Understanding how fishers exploit
multiple heterogeneously distributed fish populations with different catch
limits or conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to species targeting in fisheries resulting in preferential sampling
\citep{Martinez-Minaya2018}. Often data are aggregated or extrapolated which
requires assumptions about the spatial and temporal scale of processes. Our
study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatio-temporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
\citep{Dunn2016}, understanding assumptions behind the data used -
increasingly a combination of logbook and positional information from vessel
monitoring systems - is vital to ensure measures are effective. \\

@@

Our approach captures fine scale population and fishery dynamics and their
interaction in a way not usually possible with real data and thus not usually
considered in fisheries simulations. While other simulation frameworks seek to
model individual vessel dynamics based on inferred dynamics from VMS and
logbook records \citep{Bastardie2010}, or as a system to identify measures to
meet particular management goals \citep{Bailey2018}, our framework allows users
to explore the assumptions in modelling observations data and evaluate the
underlying dynamics of such approaches at a fine spatial and temporal scale.
This offers the advantage that larger scale fishery patterns are emergent
properties of the system rather and results can be compared to those obtained
under a statistical modelling framework. \\

Our results demonstrate the importance of data scale and resolution when using
observational data to support management measures. In doing so it highlights  
depends on scale of process: pop movement etc... Important to consider how
fishers interact / adapt to changes with the resource and mgmt. \\
